 

### 2022-03-04 doc/manuscript/tables_figures/schematic_summary.Rmd
updated schematic summary table
@teixeirak  less than or equal to 3% looks good.

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
*not biologically significant

>>>>

#add footnote: 
#kableExtra::footnote(number = c("'RP' and 'DP' refer to ring- and diffuse- porous species, respectively", "'-' and '+' = significant negative or positive response, respectively; 'n.s.'= no significant correlation"), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
*While this result was statistically significant, effect size was small (estimated change $\le 3$%/$^\circ$C) and considered not biologically significant
